---
title: "getting the twitter data"
output:
  pdf_document: default
  html_document: default
authors: Sammy Salustri and Yagmur Idil Ozdemir
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(twitteR)
library(tm)
library(readxl)
library(dplyr)
library(readr)
```

##Get Access to twitter Data: We created credentials for "Politicians Language Analysis." App ID is 15958126.  

```{r}

consumer_key <- ""
consumer_secret<- ""
access_token <- ""
access_secret <- ""
#github got mad at me for posting these when I pushed this file. I have the actual numbers on my computer.

setup_twitter_oauth(consumer_key ,consumer_secret,access_token ,access_secret)
```

## Create dataset containing all tweets of all politicians and the times they were created. For preliminary testing to make sure all twitter accounts are accessible and for run-time concerns, we only take in one tweet per politician. We will change this. 

```{r }

politicians_df<-read_xlsx("politicians.xlsx")
handles<-politicians_df$Twitter

get_tweets<- function(user) {
  user_data<-userTimeline(user, n=1, includeRts=FALSE)
  result_df<- twListToDF(user_data) %>% select(text, created,screenName)
  return(result_df)
}

all_data<-rbind(lapply(handles, FUN=get_tweets))
results<-do.call("rbind", all_data)

```

## Return the frequency of the words that are parsed from each tweet, returned as a list. We clean the data from any punctuation, turn words to lower case and exclude stopwords. 

```{r}
#split_data <- strsplit(user_data$text, split=" ")
freq <- termFreq(results$text, control = list(removePunctuation = TRUE, tolower = TRUE, stopwords = TRUE))

```


##Get csv files for running personality test on freq words
```{r}
#make library five personality, with one column referring to trait 

library_conscientiousness <- read_csv('http://wwbp.org/downloads/public_data/C.top100.1to3grams.gender_age_controlled.rmatrix.csv') %>% mutate(trait = "conscientiousness") %>% select(-con)
library_openness <- read_csv('http://wwbp.org/downloads/public_data/O.top100.1to3grams.gender_age_controlled.rmatrix.csv') %>% mutate(trait = "openness") %>% select(-ope)
library_agreeableness <- read_csv('http://wwbp.org/downloads/public_data/A.top100.1to3grams.gender_age_controlled.rmatrix.csv') %>% mutate(trait = "agreeableness") %>% select(-agr)
library_extraversion <- read_csv('http://wwbp.org/downloads/public_data/E.top100.1to3grams.gender_age_controlled.rmatrix.csv') %>% mutate(trait = "extraversion") %>% select(-ext)
library_neuroticism  <- read_csv('http://wwbp.org/downloads/public_data/N.top100.1to3grams.gender_age_controlled.rmatrix.csv') %>% mutate(trait = "neuroticism") %>% select(-neu)

library_fivepersonality <- rbind(library_agreeableness,library_conscientiousness,library_extraversion, library_neuroticism, library_agreeableness)


```


##Get sentiment libraries in R for word/sentence sentiment : positive/negative ex.
```{r}
install.packages("devtools")
library("devtools")
install_github("cran/SentimentAnalysis")
library(SentimentAnalysis)
library(tidytext)
str(sentiments)

#examples -- proof of concept
#sentiment <- analyzeSentiment("I really hate doing screeening on zebrafish.")
#sentiment$SentimentQDAP
#[1] -0.25
#sentiment <- analyzeSentiment("Knowing I go back home in 2 weeks makes studying easier")
# sentiment$SentimentQDAP
#[1] 0.1428571
# sentiment <- analyzeSentiment("I cannot believe I won that lottery. Dreams do come true!")
# sentiment$SentimentQDAP
#[1] 0.5
#analyzeSentiment() does wordcount, uncertainity also
#there are multiple dictionaries inside, this is QDAP scores. 
```

##This has subjectivity : https://www.r-bloggers.com/slightly-more-than-basic-sentiment-analysis/